---
title: "BMA with Different Distance Measures"
format: html
filters:
  - /home/max/_extensions/tarleb/parse-latex/parse-latex.lua
---

---


::: {.callout-note collapse="true" icon="false" appearance="simple"}
### Replication of Original Table II from Paper

```{r header, echo = FALSE}

pacman::p_load(
  dplyr,
  magrittr,
  haven,
  fixest,
  BMS
)

rm(list=ls())

data_path <- "../data/source/Tables"
```

```{r replicate_table_2, echo = FALSE, results="asis", message = FALSE, warnings = FALSE}
# Read in Data ------------------------------------------------------------

literacy_data <- read_dta(file.path(data_path, "Literacy Argentina Brazil Paraguay.dta"))

literacy_data <- literacy_data %>%
  mutate(mesorregi = as.factor(mesorregi))

# Re-Run the Regression from the Paper ------------------------------------

# Full sample
model_full_1 <- feols(illiteracy ~ distmiss + lati + longi + corr + ita + mis + mis1, data = literacy_data)
model_full_2 <- feols(illiteracy ~ distmiss + lati + longi + area + tempe + alti + preci + rugg + river + coast + corr + ita + mis + mis1, data = literacy_data)

# Brazil
brazil_data <- literacy_data %>% filter(country == "BRA")
model_brazil_1 <- feols(illiteracy ~ distmiss + lati + longi + mesorregi, data = brazil_data)
model_brazil_2 <- feols(illiteracy ~ distmiss + lati + longi + area + tempe + alti + preci + rugg + river + coast + mesorregi, data = brazil_data)

# Argentina
argentina_data <- literacy_data %>% filter(country == "Argentina")
model_argentina_1 <- feols(illiteracy ~ distmiss + lati + longi + corr, data = argentina_data)
model_argentina_2 <- feols(illiteracy ~ distmiss + lati + longi + area + tempe + alti + preci + rugg + river + coast + corr, data = argentina_data)

# Paraguay
paraguay_data <- literacy_data %>% filter(country == "Paraguay")
model_paraguay_1 <- feols(illiteracy ~ distmiss + ita, data = paraguay_data)
model_paraguay_2 <- feols(illiteracy ~ distmiss + area + tempe + alti + preci + rugg + river + coast + ita, data = paraguay_data)


# Display outputs
etable(
  model_full_1, 
  model_full_2, 
  model_brazil_1, 
  model_brazil_2, 
  model_argentina_1, 
  model_argentina_2, 
  model_paraguay_1, 
  model_paraguay_2,
  se = "hetero",
  tex = TRUE
)
```
:::

## BMA with Linear Distance

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r linear, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

literacy_matrix <- cbind(
  literacy_data$illiteracy,
  literacy_data$distmiss,
  literacy_data$lati,
  literacy_data$longi,
  literacy_data$corr,
  literacy_data$ita,
  literacy_data$mis,
  literacy_data$mis1,
  literacy_data$area,
  literacy_data$tempe,
  literacy_data$alti,
  literacy_data$preci,
  literacy_data$rugg,
  literacy_data$river,
  literacy_data$coast,
  literacy_data$distfran
)

colnames(literacy_matrix) <- c(
  "illiteracy",
  "distmiss",
  "lati",
  "longi",
  "corr",
  "ita",
  "mis",
  "mis1",
  "area",
  "tempe",
  "alti",
  "preci",
  "rugg",
  "river",
  "coast",
  "distfran"
)

bmalit = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r linear_image, echo = FALSE}
image(bmalit[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r linear_density, echo = FALSE}
density(bmalit)
```
:::


## BMA with Linear Distance, Fixed Distance Inclusion

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r linearf, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

bmalitf = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T,
  fixed.reg = "distmiss"
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r linearf_image, echo = FALSE}
image(bmalitf[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r linearf_density, echo = FALSE}
density(bmalitf)
```
:::


## BMA with Exponential Distance (λ = 1/200)

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r exp, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

literacy_matrix <- cbind(
  literacy_data$illiteracy,
  exp(-literacy_data$distmiss/200),
  literacy_data$lati,
  literacy_data$longi,
  literacy_data$corr,
  literacy_data$ita,
  literacy_data$mis,
  literacy_data$mis1,
  literacy_data$area,
  literacy_data$tempe,
  literacy_data$alti,
  literacy_data$preci,
  literacy_data$rugg,
  literacy_data$river,
  literacy_data$coast,
  exp(-literacy_data$distfran/200)
)

colnames(literacy_matrix) <- c(
  "illiteracy",
  "distmiss_exp",
  "lati",
  "longi",
  "corr",
  "ita",
  "mis",
  "mis1",
  "area",
  "tempe",
  "alti",
  "preci",
  "rugg",
  "river",
  "coast",
  "distfran_exp"
)

bmalit = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r exp_image, echo = FALSE}
image(bmalit[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r exp_density, echo = FALSE}
density(bmalit)
```
:::


## BMA with Exponential Distance (λ = 1/200), Fixed Distance Inclusion

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r expf, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

bmalitf = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T,
  fixed.reg = "distmiss_exp"
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r expf_image, echo = FALSE}
image(bmalitf[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r expf_density, echo = FALSE}
density(bmalitf)
```
:::

## BMA with Logarhitmic Distance

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r log, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

literacy_matrix <- cbind(
  literacy_data$illiteracy,
  log(literacy_data$distmiss),
  literacy_data$lati,
  literacy_data$longi,
  literacy_data$corr,
  literacy_data$ita,
  literacy_data$mis,
  literacy_data$mis1,
  literacy_data$area,
  literacy_data$tempe,
  literacy_data$alti,
  literacy_data$preci,
  literacy_data$rugg,
  literacy_data$river,
  literacy_data$coast,
  log(literacy_data$distfran)
)

colnames(literacy_matrix) <- c(
  "illiteracy",
  "distmiss_log",
  "lati",
  "longi",
  "corr",
  "ita",
  "mis",
  "mis1",
  "area",
  "tempe",
  "alti",
  "preci",
  "rugg",
  "river",
  "coast",
  "distfran_log"
)

bmalit = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r log_image, echo = FALSE}
image(bmalit[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r log_density, echo = FALSE}
density(bmalit)
```
:::


## BMA with Logarithmic Distance, Fixed Distance Inclusion

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r logf, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

bmalitf = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T,
  fixed.reg = "distmiss_log"
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r logf_image, echo = FALSE}
image(bmalitf[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r logf_density, echo = FALSE}
density(bmalitf)
```
:::

## BMA with Gaussian Distance (exp(-(d²)/(2*100²)))

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r gau, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

literacy_matrix <- cbind(
  literacy_data$illiteracy,
  exp(-(literacy_data$distmiss^2)/(2*100^2)),
  literacy_data$lati,
  literacy_data$longi,
  literacy_data$corr,
  literacy_data$ita,
  literacy_data$mis,
  literacy_data$mis1,
  literacy_data$area,
  literacy_data$tempe,
  literacy_data$alti,
  literacy_data$preci,
  literacy_data$rugg,
  literacy_data$river,
  literacy_data$coast,
  exp(-(literacy_data$distfran^2)/(2*100^2))
)

colnames(literacy_matrix) <- c(
  "illiteracy",
  "distmiss_gau",
  "lati",
  "longi",
  "corr",
  "ita",
  "mis",
  "mis1",
  "area",
  "tempe",
  "alti",
  "preci",
  "rugg",
  "river",
  "coast",
  "distfran_gau"
)

bmalit = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r gau_image, echo = FALSE}
image(bmalit[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r gau_density, echo = FALSE}
density(bmalit)
```
:::


## BMA with Gaussian Distance (exp(-(d²)/(2*100²))), Fixed Distance Inclusion

::: {.callout-tip collapse="true" icon="false"}
### Raw Output
```{r gauf, echo = FALSE, warnings = FALSE}
# Slap a BMA on it --------------------------------------------------------

bmalitf = bms(
  X.data = literacy_matrix,
  burn = 10000,
  iter = 100000,
  nmodel = 100, 
  mprior="fixed", 
  g="UIP",  
  mprior.size=7, 
  user.int=T,
  fixed.reg = "distmiss_gau"
)
```
:::

::: {.callout-warning collapse="true" icon="false"}
### Image
```{r gauf_image, echo = FALSE}
image(bmalitf[1:100],F) 
```
:::

::: {.callout-note collapse="true" icon="false"}
### Density Plots
```{r gauf_density, echo = FALSE}
density(bmalitf)
```
:::

